%-------------------------
% Resume in Latex
% Author : Matty
% Based on: https://github.com/jakegut/resume (which was itself based on https://github.com/sb2nov/resume)
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}

\input{glyphtounicode}

% -------------------- FONT OPTIONS --------------------
% sans-serif
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% serif
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in} % Default was -.5in
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{4.08003pt}

% -------------------- START OF DOCUMENT --------------------
\begin{document}

% -------------------- HEADING--------------------
\begin{flushright}
  % \vspace{-4pt}
  \color{gray}
  \item
  Last Updated on January 19th, 2024
\end{flushright}

\vspace{-5pt}

\begin{center}
  \textbf{\Huge \scshape KaiYi Chang (Oscar)} \\ \vspace{8pt}
  \small
  \faIcon{github}
  \href{https://github.com/Oschangkai}{\underline{github.com/Oschangkai}} $  $
  \faIcon{code}
  \href{https://kaiyeee.tw/resume}{\underline{kaiyeee.tw/resume}} $  $
  \faIcon{linkedin}
  \href{https://linkedin.com/in/kaiyeee}{\underline{linkedin.com/in/kaiyeee}} $  $
  \faIcon{envelope}
  \href{mailto:me@yi.contact}
  {\underline{me@yi.contact}}
\end{center}

% -------------------- EDUCATION --------------------
\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
{National Taiwan University of Science and Technology}{Sep. 2021 - Present}
{M.S. Information Management}{}
\vspace{0.5pt}
\resumeItemListStart
\resumeItem{Teaching assistant in four courses: Java Object-Oriented Programming, Golang Programming, Introduction to Cloud Application Security, and Information Security Management.}
\resumeItem{Served as the lab network administrator and managed the development and maintenance of the College of Management's systems.}
\resumeItemListEnd

\resumeSubheading
{Yuan Ze University}{Sep. 2015 - June 2019}
{B.S. Information Management}{}
\resumeItemListStart
\resumeItem{Student Dormitory Network Administrator}{2016 -- 2018}
\resumeItem{Information Technology Association Club (ITAC) - 3rd Director}{2016}
\resumeItem{Academic Section Head of Student Association of Information Management Department}{2016}
\resumeItemListEnd

\vspace{1pt}

% \subsection{Coursework}
% \textbf{Courses:} Object-Oriented Programming, Data Structures \& Algorithms, Embedded Systems, Discrete Math, Linear Algebra, Calculus, Physics, Probability \& Statistics \\
% \textbf{Awards:} Dean's Honor List (3x), AP Scholar with Distinction (2x), World Language History Award (Spanish)

\resumeSubHeadingListEnd

% -------------------- SKILLS --------------------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
                \textbf{Services}{: Azure, Azure DevOps, Microsoft 365 } \\
                \textbf{Languages}{: C\#, Java, JavaScript/TypeScript, HTML/CSS, Python } \\
                \textbf{Frameworks}{: .NET Core, Angular } \\
                \textbf{Focus on}{: Cloud, DevOps, Web Development } \\
          }}
\end{itemize}


% -------------------- WORK EXPERIENCE --------------------
\section{Work Experience}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Freelancer}\vspace{8pt} $|$ \footnotesize\emph{Student}}{Sep. 2021 -- Present}
{\small{}}
\resumeItemListStart
\resumeItem{\textbf{AACSB Certification System}: I developed a system for the College of Management to help the certification process and generate all reports.}
\resumeItem{\textbf{International Shipping Company: Automation Deployment}: I use Jenkins to build and deploy the customer's system, including different environments to global sites.}
\resumeItem{\textbf{Office of Real Estate Office Network Planning}: Two-story office network equipment planning, including network deployment, guest network and firewall settings, and NAS setup.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{MAYO Human Capital}\vspace{8pt} $|$ \footnotesize\emph{Cloud Technical Engineer}}{Mar. 2021 -- Sep. 2021}
\small{Internal System Development and Network Administration}
\resumeItemListStart
\resumeItem{I Develop a simple system for monitoring company services and operating scattered resources on the cloud, achieving more detailed permission control than Azure. (.Net Core 3, Angular 12)}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{WiAdvance Technology Co.} $|$ \footnotesize\emph{Senior Software Engineer}\vspace{8pt}}{Feb. 2019 -- Mar. 2021}
{\small{POC Projects using Azure and Act As a only DevOps Engineer in the company.}}
\vspace{-3pt}
\resumeItemListStart
\resumeItem{Microsoft Power Platform hackathon lecturer, e.g., \href{https://news.microsoft.com/zh-tw/npo-power-platform/}{\underline{non-profit organizations.}}.}
\resumeItem{\textbf{Customer Billing Data ETL \& Visualization}: I used Azure Data Factory to capture, convert, and calculate CSP data. I then utilized Power BI to present the customers' usage charts, successfully assisting them in checking their billing accounts, identifying usage issues, and providing recommendations.}
\resumeItem{\textbf{Licensing Key Management \& Release}: Build a serverless licensing key management system using Logic Apps, Storage Account, API Management, Azure CDN, Azure Functions, Key Vault, and Azure SQL.}
\resumeItem{\textbf{Time Sheet Data ETL System}: A (semi) automated timesheet form-filling system using Azure Data Factory to capture and process data from Microsoft 365 and follow up with Azure Functions to do the final data batch conversion.}
\resumeItem{\textbf{Manufacturing Monitor System}: A pure containerized system that can deploy services into cloud service (App Service, Azure Container Registry, Azure SQL ... etc.) and local machines using Azure DevOps.}
\resumeItemListEnd


\resumeProjectHeading
{\textbf{Accudata} $|$ \footnotesize\emph{MIS / SE Intern}\vspace{8pt}}{Feb. 2018 -- Feb. 2019}
{\small{IDC Equipment Management, Network Administration, and Network re-architecture}}

% \vspace{3px}
% Some projects are omitted; detailed work projects are listed \href{https://kaiyeee.tw/resume/experience.html}{\underline{here}} (in Chinese).

\resumeSubHeadingListEnd

% -------------------- PROJECTS --------------------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{AACSB Certification System} $|$ \footnotesize\emph{C\#, .NET Core, Angular, Flatcar Container OS}}{Jul. 2022 -- Present}
\resumeItemListStart
\resumeItem{\href{https://github.com/Oschangkai/aacsb-api}{\underline{GitHub Repository - Frontend}}}
\resumeItem{\href{https://github.com/Oschangkai/aacsb-web}{\underline{GitHub Repository - Backend}}}
\resumeItemListEnd

% \resumeProjectHeading
% {\textbf{FoodDropper} $|$ \footnotesize\emph{Java, Maven, API (Spigot), Git, IntelliJ IDEA}}{Aug. 2022}
% \resumeItemListStart
% \resumeItem{Developed a Minecraft server plugin to limit players to one way of replenishing their hunger bar}
% \resumeItemListEnd

%% -------------------- ADDITIONAL EXPERIENCE --------------------

\subsection{Additional Projects}

\resumeProjectHeading
{\textbf{Raspberry Pi Dotnet Minimal API} $|$ \footnotesize\emph{.NET 8, Raspberry Pi, Minimal API}\vspace{8pt}}{2024}
{\small{Repo: \href{https://github.com/Oschangkai/rpi-dotnet-minimal-api}{\underline{GitHub}}}}
\vspace{3px}

\resumeProjectHeading
{\textbf{Slides}\vspace{8pt}}{ }
{\small{Link: \href{https://slides.kaiyeee.tw}{\underline{https://slides.kaiyeee.tw}}}}
\vspace{3px}

\resumeProjectHeading
{\textbf{Data Journalism} $|$ \footnotesize\emph{Web, Data Analysis}\vspace{8pt}}{2018}
{\small{Link: \href{https://datajournalism.kaiyeee.tw}{\underline{https://datajournalism.kaiyeee.tw}}, Repo: \href{https://github.com/Oschangkai/datajournalism}{\underline{GtiHub}}}}
\vspace{3px}

\resumeProjectHeading
{\textbf{22nd InnoServe Awards, Taoyuan Open Data - TripTao} $|$ \footnotesize\emph{Honorable Mention}\vspace{8pt}}{2017}
{\small{Link: \href{https://triptao.kaiyeee.tw}{\underline{https://triptao.kaiyeee.tw}}, Repo: \href{https://github.com/Oschangkai/Triptao-Web}{\underline{GtiHub}}}}
\vspace{3px}

\resumeProjectHeading
{\textbf{2016 YZU IC,IM,CS Orientation -- Official Website} $|$ \footnotesize\emph{Web}\vspace{8pt}}{2016}
{\small{Link: \href{https://yzu2016camp.kaiyeee.tw}{\underline{https://yzu2016camp.kaiyeee.tw}}, Repo: \href{https://github.com/Oschangkai/yzu2016camp}{\underline{GtiHub}}}}
\vspace{3px}

\resumeProjectHeading
{\textbf{Information Technology Association Club (ITAC) -- Official Website} $|$ \footnotesize\emph{Web}\vspace{8pt}}{2016}
{\small{Repo: \href{https://github.com/Oschangkai/itac}{\underline{GtiHub}}}}
\vspace{3px}


\subsection{Hobbies}

\resumeProjectHeading
{\textbf{HomeLab}\vspace{8pt}}{Late 2022 -- Present}
{\small{Running home automation, containerized services, and virtualization in 12 hosts. Config files will soon be open source.}}

\resumeSubHeadingListEnd

\end{document}